Title

### 2023-04-21 main.tex
Fix the fixes
Pipeline goes brrrrrrr
Cambios sec 1 y 2

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section*{Introduction} % {{{

% }}}
\section{Pauli Channels}  \label{sec: Pauli Channels} % {{{
\cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
hay mencion a los quantum channels. Menos
cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
por lo menos leido y aprobado en principio de mi parte.} we introduce the
concept of quantum channels, focusing on a specific type called Pauli channels.
Furthermore, we define Pauli dynamical maps, which
are curves of Pauli channels parametrized by a variable.
% }}}
\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{

@@

\cpnote{Le hice un par de cambios pequeños pero la veo bastante bien. }
% }}}
\subsection*{Pauli Channels} \label{subsec: Pauli Channels} % {{{

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting eq. (\ref{eq:  Density matrix Nqbit}) in eq. (\ref{eq: pauli channel N-qubit})
and using the property of eq. (\ref{eq: propiedad-pauli}):
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
% }}}
\subsection*{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

\cpnote{aca voy}

@@

In this section we propose a quantum circuit that 
simulates N-qubit Pauli channels.
Furthermore, we show the results of implementing the circuit for $N=1$ on
a quantum computer. 
\cpnote{esto está un poco desordenado y a un ritmo creo qeu inapropiado por lo rapido}

To create the circuit, we remember that a Pauli channel as in eq.~(\ref{eq: pauli channel N-qubit})
applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
Given this, it is easy to construct a quantum circuit that implements 
a Pauli channel with the help of $2N$ ancilla qubits,
the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.$

@@

\cpnote{paro aca de leer}

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1} }} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=7]{$|\vec{\gamma} \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & & & & & \\
\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on $2N$ ancilla qubits and then uses them to apply
all possible Pauli strings on the principal qubits
with probabilities $k_{\vec{\gamma}}$.}
\label{fig: circuit-pauli}
\end{figure}

@@

\subsection*{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in fig. (\ref{fig: citcuit-pauli-1}),
 which is a special case of fig. (\ref{fig: circuit-pauli}).

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}. {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
we sampled $249$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, we used quantum process tomography to obtain the
Choi matrix corresponding to the implementation of the circuit~\cite{Chuang:1996}.
Then, we compared this Choi matrix with the theoretical
Choi matrix of the channel we were implementing by calculating the 
process fidelity~\cite{Jozsa94,chuangbook} between them.
Finally, using the representation of Pauli channels in a tetrahedron as
in eq.~(\ref{eq: conditions-tetrahedron}),
we show the fidelities for these channels in fig.~(\ref{fig: fidelity one qubit}).
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel.
\tbnote{Puedo cambiar la fidelidad por otras distancias, como la diamond norm,
pero estoy buscando cuál conviene más.}}w
\label{fig: fidelity one qubit}
\end{figure}

% }}}
% }}}
\section*{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}

\textbf{Puntos:}
\begin{itemize}
\item As said before, to implement a Pauli dynamical map, 
we need to create the parametrized $2n$-qubit state 
$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
\item However, creating this state will in general require many rotations parametrized by $p$. 
For example, for the case of a Pauli dynamical map on 1 qubit, 
the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
In general, to create a parametrized state on $2n$ ancilla qubits will require
$2n-1$ rotations parametrized by $p$.
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
aunque se puede y debe achicar bastante.
\end{itemize}
% }}}
\section*{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
Lo tengo para parabolic y para depolarizing.
\end{itemize}
% }}}
\section*{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}

\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita. Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$. Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis. 
\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
\begin{itemize}
\item Cualquier matriz $H$ de un qubit cumple el teorema.
\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
\end{itemize}
\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
\end{itemize}
% }}}
\section*{Conclusion} % {{{

@@

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.
% }}}
\section*{Supporting information} % {{{

@@

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}
\section*{Acknowledgments} % {{{
Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
acknowledged.

>>>>

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section{Introduction} % {{{

% }}}
\section{Quantum Channels}  \label{sec: Pauli Channels} % {{{
\cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
\tbnote{Lo cambié}
\cpnote{El texto esta bien, pero creo qeu la distribucino de subsecciones esta chistosna y 
los titulo tambien. Platicar con Tomas a ver a que llegamos. }

% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
hay mencion a los quantum channels. Menos
cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
por lo menos leido y aprobado en principio de mi parte.} we introduce the
concept of quantum channels, focusing on a specific type called Pauli channels.
Furthermore, we define Pauli dynamical maps, which
are curves of Pauli channels parametrized by a variable.
% }}}
%\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{

@@

\cpnote{Le hice un par de cambios pequeños pero la veo bastante bien. }
\tbnote{Perfecto, gracias!}
% }}}
\subsection{Pauli Channels} 
\label{subsec: Pauli Channels} % {{{

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting eq. (\ref{eq:  Density matrix Nqbit}) in eq. (\ref{eq: pauli channel N-qubit})
and using the property of eq. (\ref{eq: propiedad-pauli}):
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
% }}}
\subsection{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

@@

\cpnote{Acá voy}

In this section we propose a quantum circuit that simulates N-qubit Pauli
channels.  Furthermore, we show the results of implementing the circuit for
$N=1$ on a quantum computer.

To create the circuit, we remember that a Pauli channel as the one in eq.~(\ref{eq: pauli channel N-qubit})
applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
Given this, it is easy to construct a quantum circuit that implements 
a Pauli channel with the help of $2N$ ancilla qubits,
the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.

@@

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma}}} \gategroup[wires=2,steps
=1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
\gategroup[wires=2,steps
=1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
{$|\vec{\gamma}\rangle$} & \qw \\
\lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
% \gategroup[wires=1,steps
%=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
& \qw 
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$. 
Then, for every vector $\vec{\gamma}$, it applies the operator $\sigma_{\vec{\gamma}}$ 
if the ancilla qubits are in the state $\vec{\gamma}$.}
\label{fig: circuit-pauli}
\end{figure}

@@

\subsection{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in fig. (\ref{fig: citcuit-pauli-1}),
 which is a special case of fig. (\ref{fig: circuit-pauli})
 but with all qubits explicitly shown.

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$\tilde{q}_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$\tilde{q}_1$} & \gateinput{$\;\;\;\;\;b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}. {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
we sampled $249$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, we used quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the
Choi matrix corresponding to the implementation of the circuit $\mathcal{C}_{I}$.
Then, we compared this Choi matrix with the theoretical
Choi matrix $\mathcal{C}_T$ of the channel we wanted to implement.

To make this comparison, we used the diamond norm~\cite{Aharonov},
which allows us to discriminate between quantum channels.
Suppose an agent is given one of the channels $\mathcal{C}_I$, $\mathcal{C}_T$
with probability $1/2$ for each,
and tries to guess which channel they received
by passing through it a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{succ} = \dfrac{1}{2}+ \dfrac{1}{2} ||\mathcal{C}_I - \mathcal{C}_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm.
Notice that $p_{succ}=1/2$ means that the channels
are indistinguishable, while $p_{succ}=1$
indicates that they are perfectly distinguishable.

Finally, using the representation of Pauli channels in a tetrahedron as
in eq.~(\ref{eq: conditions-tetrahedron}),
we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of success defined by eq. (\ref{eq: probability-success}) for the channels analyzed.
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Maximal probabilities of success for one-qubit Pauli channel} $p_{succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the distinguishability of each channel's implementation using the circuit for a 1-qubit Pauli channel.}
\label{fig: fidelity one qubit}
\end{figure}

\newpage
% }}}
% }}}
\section{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}

\textbf{Puntos:}
\begin{itemize}
\item As said before, to implement a Pauli dynamical map, 
we need to create the parametrized $2n$-qubit state 
$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
\item However, creating this state will in general require many rotations parametrized by $p$. 
For example, for the case of a Pauli dynamical map on 1 qubit, 
the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
In general, to create a parametrized state on $2n$ ancilla qubits will require
$2n-1$ rotations parametrized by $p$.
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
aunque se puede y debe achicar bastante.
\end{itemize}
% }}}
\section{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
Lo tengo para parabolic y para depolarizing.
\end{itemize}
% }}}
\section{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}

\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita. Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$. Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis. 
\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
\begin{itemize}
\item Cualquier matriz $H$ de un qubit cumple el teorema.
\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
\end{itemize}
\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
\end{itemize}
% }}}
\section{Conclusion} % {{{

@@

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.
% }}}
\section{Supporting information} % {{{

@@

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}
\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
acknowledged.
